plyranges: a grammar for manipulating genomics data

### 2018-02-12 paper.Rmd
outline of design and implementation

### Core verbs

@@

### Arithimetic

@@

The _plyranges_ package is avaiable on the Bioconductor project website 
[https://bioconductor.org](https://bioconductor.org) or can be accessed
via Github [https://github.com/sa-lee/plyranges](https://github.com/sa-lee/plyranges).
We aim to continue developing the `plyranges` package and extend it for use
with more complex data structures outside of genomics such as the 
_SummarizedExperiment_ class. As the `plyranges` interface encourages tidy data 
practices it also integrates well with the grammar of graphics, we aim to use
it for the visualisation of genomic ranges.

>>>>

### Construction and Import/Output

The _plyranges_ API provides the methods `as_granges()` and `as_iranges()`
for constructing Ranges from tabular data structures, such as data.frames in
base R. These methods use non-standard evaluation so columns in a data.frame
can be modified before a Ranges object is created.

The package also provides a consistent framework for reading and writing 
files from and to common genomic data formats, using the `rtracklayer` package
as a backend. The methods are implemented in the `read_/write_` family of 
functions, currently _plyranges_ can read and write BAM, BED, BEDPE, 
narrowPeaks, GFF/GTF, WIG and BigWig files.

### Manipulation of Ranges

@@

### Arithimetic on Ranges

@@

The _plyranges_ package is avaiable on the Bioconductor project website 
[https://bioconductor.org](https://bioconductor.org) or can be accessed
via Github [https://github.com/sa-lee/plyranges](https://github.com/sa-lee/plyranges).
We aim to continue developing the `plyranges` package and extend it for use
with more complex data structures  such as the 
_SummarizedExperiment_ class, which can be used for analysing transcriptomic
and variant data. As the `plyranges` interface encourages tidy data 
practices it integrates well with the principles of the grammar of graphics, 
we aim to use it for the visualisation of genomic ranges.
